Figure 5 - IP-MS

### 2024-07-15 ms_figure_5_ipms.Rmd
Adapt DBD family pie charts (Fig 5)

```{r}
## Pie chart, within-vs-between DBD family interactions
pie_bait_150 <- ggplot(
    baitdata_150$nbrIntMat |>
        select(nbrTFs_samefam, nbrTFs_difffam) |>
        pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
        group_by(class) |>
        summarize(nbrTF = sum(nbrTF), .groups = "drop"),
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nhigh stringency") + 
    theme_void()
```

@@

```{r}
## Pie chart, within-vs-between DBD family interactions
pie_bait_150_loose <- ggplot(
    baitdata_150_loose$nbrIntMat |>
        select(nbrTFs_samefam, nbrTFs_difffam) |>
        pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
        group_by(class) |>
        summarize(nbrTF = sum(nbrTF), .groups = "drop"),
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nlow stringency") + 
    theme_void()
```

@@

```{r}
## Pie chart, within-vs-between DBD family interactions
pie_bait_500 <- ggplot(
    baitdata_500$nbrIntMat |>
        select(nbrTFs_samefam, nbrTFs_difffam) |>
        pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
        group_by(class) |>
        summarize(nbrTF = sum(nbrTF), .groups = "drop"),
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nhigh stringency") + 
    theme_void()
```

```{r}
## Pie chart, within-vs-between DBD family interactions
pie_bait_500_loose <- ggplot(
    baitdata_500_loose$nbrIntMat |>
        select(nbrTFs_samefam, nbrTFs_difffam) |>
        pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
        group_by(class) |>
        summarize(nbrTF = sum(nbrTF), .groups = "drop"),
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nlow stringency") + 
    theme_void()
```

@@

>>>>

```{r}
## Expected fraction of 'same family' pairs
famtbl <- table(baitdata_150$nbrIntMat |>
                    filter(dbdfam != "Other" & 
                               bait != "Untagged") |>
                    pull(dbdfam))
nbait <- sum(baitdata_150$nbrIntMat$bait != "Untagged")
(exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1)))

## Pie chart, within-vs-between DBD family interactions
pie_data_150 <- baitdata_150$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop")
pie_bait_150 <- ggplot(
    pie_data_150,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_150$nbrTF),
                 linewidth = 1.5) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nstrict cutoff") + 
    theme_void()
```

@@

```{r}
## Expected fraction of 'same family' pairs
famtbl <- table(baitdata_150_loose$nbrIntMat |>
                    filter(dbdfam != "Other" & 
                               bait != "Untagged") |>
                    pull(dbdfam))
nbait <- sum(baitdata_150_loose$nbrIntMat$bait != "Untagged")
(exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1)))

## Pie chart, within-vs-between DBD family interactions
pie_data_150_loose <- baitdata_150_loose$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop")
pie_bait_150_loose <- ggplot(
    pie_data_150_loose,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_150_loose$nbrTF),
                 linewidth = 1.5) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nlenient cutoff") + 
    theme_void()
```

@@

```{r}
## Expected fraction of 'same family' pairs
famtbl <- table(baitdata_500$nbrIntMat |>
                    filter(dbdfam != "Other" & 
                               bait != "Untagged") |>
                    pull(dbdfam))
nbait <- sum(baitdata_500$nbrIntMat$bait != "Untagged")
(exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1)))

## Pie chart, within-vs-between DBD family interactions
pie_data_500 <- baitdata_500$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop")
pie_bait_500 <- ggplot(
    pie_data_500,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_500$nbrTF),
                 linewidth = 1.5) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nstrict cutoff") + 
    theme_void()
```

```{r}
## Expected fraction of 'same family' pairs
famtbl <- table(baitdata_500_loose$nbrIntMat |>
                    filter(dbdfam != "Other" & 
                               bait != "Untagged") |>
                    pull(dbdfam))
nbait <- sum(baitdata_500_loose$nbrIntMat$bait != "Untagged")
(exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1)))

## Pie chart, within-vs-between DBD family interactions
pie_data_500_loose <- baitdata_500_loose$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop")
pie_bait_500_loose <- ggplot(
    pie_data_500_loose,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_500_loose$nbrTF),
                 linewidth = 1.5) + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nlenient cutoff") + 
    theme_void()
```

@@

The pie charts below display the number of observed within- and between-DBD 
family interactions under different salt conditions and using different 
thresholds for identifying interactions. The black arc indicate the  
fraction of within-DBD family interactions expected by chance.
